Deep Probabilistic Models for Camera Geo-Calibration

### 2018-09-17 chapters/discussion/discussion.tex
minor change

The goal of geo-calibration is to learn the camera pose, location and
the time when the image was captured.
Our thesis focused on developing deep geo-calibration algorithms for
image understanding.
Compared to previous work, our approaches give
probabilistic outputs that are more flexible and are able to handle
the uncertainty of the scene better.

In \chapref{mcmc}, we proposed a flexible model to compute the
probability over all geo-calibration parameters. In the high
dimensional space of geo-calibration parameters, we defined an score
function for every point in that space, to measure how well the
geo-calibration parameters match the content of the input image. The
score function is defined as a weighted summation of a series of
constraint functions, and is proportional to the probability density
function of the distribution. Since xxx is computationally
intractable, in order to xxx, we approximated the probability
density function using MCMC method.
\todo{why grid method doesn't work here}
\todo{evaluation}

@@

This thesis proposed a probability model for image geo-calibration. 
Overall, we hope our work can provide xxx.

>>>>

The goal of geo-calibration is to learn the camera pose, location and
the time when the image was captured.
Our thesis focused on developing deep geo-calibration algorithms for
image understanding.
Compared to previous work, our approaches output probabilistic
predictions that are able to handle the uncertainty of the scene
better. Furthermore, we also show that
learning to geo-calibrate a camera allows us to implicitly learn to
understand the content of the scene.

In \chapref{mcmc}, we proposed a flexible model to compute the
probability over all geo-calibration parameters. In the high
dimensional space of geo-calibration parameters, we defined an score
function for every point in that space, to measure how well the
geo-calibration parameters match the content of the input image. The
score function is defined as a weighted summation of a series of
constraint functions, and is proportional to the probability density
function of the distribution. Since xxx is computationally
intractable, in order to xxx, we approximated the probability
density function using MCMC method.

@@

This thesis proposed a probabilistic model for image
geo-calibration.
The key to the success of this model is to find constraint
functions that describe the relationship between geo-calibration
parameters and the image content. We developed constraint
functions for different set of parameters that can fit to the model.
Furthermore, we also show that learning to geo-calibrate cameras helps learning
useful features for image understanding.
There are several possible future research directions for extending
this work, including: exploiting map data in cross-view learning,
replacing the CNN networks in our algorithms with Bayesian neural
networks (BNNs).
Overall, we hope our work can provide new ways for geo-calibration and
pre-task training.
